---
title: "R in 3 Months: Understanding the docs"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r child = "setup.Rmd"}
```

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
```

# Why do docs pages exist?

CRAN **requires** that every function (and dataset) in a package has a documentation page.

--

This means docs pages are ***not*** written to be read by human beings - they're designed to pass a bunch of automated tests.

--

<br>

... except some developers put a lot of effort into trying to make their documentation as helpful as possible.

---

### All function docs pages have these sections

- **Description**

  - A sentence to describe what the function does / or how to use the function.
  
--

- **Usage statement**

  - This shows the named arguments and their default values.
  
--

- **Arguments**

  - This documents how to use each argument introduced in the Usage section.

--

- **Examples**

  - There should be some useful examples of how to use the function.



