---
title: "R in 3 Months: Fall 2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

### Sep 16: Welcome

Course assignment

- Complete Getting Started

Project assignment

- None

Live session

- Intros + get to know you
- Getting Started questions
- Have previous participants talk about how they felt about learning R

### Sep 23: RMarkdown

Course assignment

- Fundamentals RMarkdown lessons

Project assignment

- Create RStudio project
- Create RMarkdown doc

Live session

### Sep 30: Data wrangling and analysis

Course assignment

- Fundamentals data wrangling lessons

Project assignment

- Do some data analysis with your data

Live session

### Oct 7: Data viz

Course assignment

- Fundamentals data viz lessons

Project assignment

- Make a graph from your data: it doesn't matter how beautiful it is!

```{r}
library(tidyverse)
msleep %>% 
  count(vore) %>% 
  ggplot(aes(x = vore,
             y = n,
             fill = vore)) +
  geom_col()
```


Live session

### Oct 14: Catch-up week (talk about best practices for their own projects)

Course assignment

- [https://rstats.wtf/project-oriented-workflow.html](https://rstats.wtf/project-oriented-workflow.html)

Project assignment

- Make your work into a project (if you didn't already do so)

Live session

- Discuss project-oriented workflow

### Oct 21: Git + GitHub

Course assignment

- See [Git + GitHub Course](https://www.notion.so/Git-GitHub-Course-a332fb84943f462faee7732c02d378d5)

Project assignment

- Get GH set up

Live session

- 

### Oct 28: Advanced data wrangling, part 1

Course assignment

- Going Deeper data wrangling lessons, part 1

Project assignment

- None

Live session

- Discuss tidy data

### Nov 4: Advanced data wrangling, part 2

Course assignment

- Going Deeper data wrangling lessons, part 2

Project assignment

- Tidy your data

Live session

- Discuss tidy data

### Nov 11: Catch-up week

Course assignment

- None

Project assignment

Live session

- Cool things you can do once you use GitHub (e.g. Netlify)

### Nov 18: Advanced data viz, part 1

Course assignment

- Going Deeper data viz lessons, part 1

Project assignment

- None

Live session

### Dec 2: Advanced data viz, part 2

Course assignment

- Going Deeper data viz lessons, part 2

Project assignment

- Take a previous plot and improve it

Live session

### Dec 9: Advanced RMarkdown

Course assignment

- Going Deeper RMarkdown lessons

Project assignment

- None

Live session

- Show ways to brand your work

### Dec 16: Final projects

~~Convert your project into some final format~~

People write a short reflection on something that has changed with their work through learning R

People post one chart they've made and we tweet them out

People could knit report and publish to RPubs

David + Charlie highlight cool things people have done

Bring in people from spring 2021 cohort to talk about what they've done with R