---
title: "R in 3 Months: Week 8 (Functions and Joins)"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r child = "setup.Rmd"}
```

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
```


# Agenda

--

1. Housekeeping

--

1. Three Tips

--

1. A Few of My Favorite Functions


--

1. Next Week

---

# Housekeeping

--

Time changes **again** next week.

--

Next week is another catch-up week. 

---

class: inverse, center, middle

# Three Tips

---

(I'll write these as I go through the feedback)

---

# Group Task

.pull-left[
Recreate this chart using this Gist:
https://rfor.us/week8groupgist
]

.pull-right[
```{r, echo=FALSE,eval=TRUE, out.height='400px', dpi=300}
spotify_songs %>% 
  group_by(playlist_genre) %>% 
  summarise(mean_duration = mean(duration_ms),
            mean_danceability = mean(danceability)) %>% 
  ggplot(aes(x = mean_duration,
             y = mean_danceability)) +
  geom_point(aes(color = playlist_genre),
             size = 4) +
  scale_color_manual(values = colors_genre) +
  theme_bw(base_size = 16)
```

]

---

class: inverse, center, middle

# A Few of My Favorite Functions

---


# Next Week

--

Catch-up week

--

Please submit anything you're working on at any point

--

No live session but there will be office hours

