---
title: "R in 3 Months: Week 8 (Functions and Joins)"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r child = "setup.Rmd"}
```

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
```


# Agenda

--

1. Housekeeping

--

1. A Few of My Favorite Functions

--

1. Group Work

--

1. Next Week

---

# Housekeeping

--

Time changes **again** next week.

--

Next week is another catch-up week. 

---

class: inverse, center, middle

# A Few of My Favorite Functions

---

class: inverse, center, middle

# Group Work

---

## Group Work

Have one person share their screen.

Copy the code from https://raw.githubusercontent.com/rfortherestofus/rin3-fall-2021/main/misc/function-exercise.R.

Working together, create a function that creates a scatterplot for any year. 

---


# Next Week

--

Catch-up week

--

Please submit anything you're working on at any point

--

No live session but there will be office hours

