---
title: "R in 3 Months: Week 3 (Data Wrangling and Analysis)"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r child = "setup.Rmd"}
```

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
library("tidyverse")
library("wakefield")
```


# Agenda

1. Housekeeping

--

1. Three Tips

--

1. Workflow Advice

--

1. Group Work

--

1. GitHub

--

1. Next Week

---

# Housekeeping

- Group check-in

???

We've had significantly fewer submissions (only 4 by Wednesday before office hours) so I'd like to do a check-in with folks about how they're doing.

I don't really have any other suggestions for house keeping. I looked at the comment on the lessons and it looks like lots of issues are being resolved there.

---

# Three Tips

1. RMarkdown output below code chunks or in the console

--

1. It's possible to add multiple arguments to mutate instead of using mutate multiple times
--

1. Processing columns that contain something like "60-80%"

???

I think it'd be useful to show that output by default goes below the code chunk but can be redirected into the console.

---

# Naming things advice

Now we're starting to work with file paths the names of files will matter more and more.

The [best and most complete advice](http://www2.stat.duke.edu/~rcs46/lectures_2015/01-markdown-git/slides/naming-slides/naming-slides.pdf) for this comes from Jenny Bryan.

But here are some tips:

- Replace spaces with a dash (`-`)

- Split parts parts of file names with _ (eg `week-2_Charlie-Hadley.Rmd`)

- Prefix numbers with `0` to aid ordering files

???

I thought this was useful to add in this week?

---

# Group Work

--

Each person share your code (either share your Gist link or by sharing your screen)

--

Presenter gives a short (~1 minute overview)

--

Others look for one thing that doesn't make sense

--

Presenter responds to questions


---

# Data Wrangling and Analysis Questions

What questions do you still have?


# Next Week

1. Course assignment: complete data viz lessons

--

1. Project assignment: make a graph from your data

