---
title: "R in 3 Months: Week 7 (Tidy Data)"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r child = "setup.Rmd"}
```

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
library("tidyverse")
library("wakefield")
library(palmerpenguins)
library(janitor)
```


# Agenda

--

1. Housekeeping

--

1. Three Tips

--

1. Group work

--

1. More about Tidy Data

--

1. Next Week

---

# Housekeeping

- Charlie's office hours on Friday instead of Wednesday

---

class: inverse, center, middle

# Three Tips

---

# XXX Need some tips XXX

---
class: inverse, center, middle

# Group Work

---

# Group Work

Copy the code from https://gist.github.com/dgkeyes/1d5ceb8b607266f1d197a218dd5c6882 into a new R script file. Then tidy the `gapminder_wide` data. 

---

class: inverse, center, middle

# Tidy Data

---

### Tidy Data is more than just the pivot_*() functions

If you're interested in the philosophy behind tidy data then [read Hadley Wickham's 2014 paper](https://doi.org/10.18637/jss.v059.i10) that introduced the concept.

<br>

The most **concise** description of tidy data is also provided by Hadley Wickham:

> "Tidy datasets are all alike, but every messy dataset is messy in its own way"
> 
> Hadley Wickham

---
class: inverse, center, middle

# Other functions for tidying data

---

# separate()

The `separate()` function is useful when a column contains **multiple variables**.

```{r, eval=TRUE}
location_data <- tribble(
  ~id, ~address,
  1, "Las Vegas, USA",
  2, "Bristol, UK",
  3, "Kassala, Sudan"
)
location_data
```

]

---

# separate()

```{r, eval=TRUE}
location_data %>% 
  separate(col = address,
           into = c("city",
                    "country"),
           sep = ", ")
```

---

## separate_rows()

The `separate_rows()` function is useful when a column contains **multiple observations of the same variable**.

---

> ###  Which of these devices do you own? Please select all that apply.

--

```{r, eval=TRUE, echo=TRUE}
device_ownership <- tribble(
  ~name, ~devices_owned,
  "Charlie", "Smart TV, Cell phone",
  "Mohammad", "Cell phone",
  "Christina", "Smart TV, Games Console, Cell phone"
)
device_ownership
```

---

```{r, eval=TRUE, echo=TRUE}
device_ownership %>% 
  separate_rows(devices_owned,
                sep = ", ")
```

---

# Next Week

--

1. There are two big topics in the next week:

  - Reducing repeatitive code with user-defined functions
  
  - Joining together datasets by shared columns
  
1. These skills will equip you to deal with more complex and larger scale data wrangling

--

1. Project assignment: XXX


