---
title: "R in 3 Months: Week 8 (Functions and Joins)"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r child = "setup.Rmd"}
```

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
library(tidycensus)
```


# Agenda

--

1. Housekeeping

--

1. Four Tips

--

1. Group work

--

1. Functions

--

1. Next Week

---

# Housekeeping

--

Time Zones changes **again** next week.

--

Next week is another catch-up week

---

class: inverse, center, middle

# Four Tips

---

(I'll write these as I go through the feedback)

---

class: inverse, center, middle

# Functions

---




---

# Next Week

--

Next week's lessons provide advice about exporting tidied raw data

--

Project assignment: (if appropriate) redesign your R project as follows:

- move raw data into the `data-raw` folder

- move your tidying script into the `data-raw` folder

- export a tidied version of your data into the `data` folder


